---
title: "STAT295-Week8"
author: "Melisa Çepni"
date: "2024-04-15"
output: html_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to R Markdown

## R Markdown

This is an `R` `Markdown` document. Markdown is a simple formatting syntax for authoring *HTML*, **PDF**, and **MS** Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

This project includes some summary statistics:

```{r cars}
summary(cars)
```

## Include Plots

```{r pressure, echo=FALSE}
plot(pressure)
# you only see the outputs echo=TRUE olunca kodlar da görünüyo
```

## List

I.  bullet list 1

II. bullet list 2

III. bullet list 3

## Format

-   superscript: 2^nd^
-   subscript: CO~2~
-   strike-through: ~~mistake~~

## Code chunk options

```{r read_gapminder, eval=FALSE, echo=FALSE}
gap <- read.csv("gapminder.csv")
```

```{r, warning=FALSE, include=TRUE, echo=FALSE}
sqrt(-1)
```

## Inline Codes

```{r, include=FALSE}
data <- mtcars
```

```{r, include=FALSE}
data <- CO2
```

I want to add some inline codes such as `r sqrt(25)`. There are `r nrow(iris)` lines in Iris data. The number of variables in iris data is `r ncol(iris)`. Here are the variables are `r names(data)`.

## Tables

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

: MyTable

```{r libraries, include=FALSE}
library(gapminder)
library(ggplot2)
library(tidyverse)
```

```{r}
top_gap <- head(gapminder)
knitr::kable(top_gap)
knitr::kable(top_gap,
             caption="The first rows of the dataset, gapminder")
```

```{r mytable1}
knitr::kable(top_gap,
             caption="The first row of the dataset, gapminder")
```

To cite the table, we can use Table \@ref(tab:mytable1)

```{r gg-oz-gapminder, fig.cap="Life Exp. from 1952-2007 for Turkey"}
gapminder %>%
  filter(country == "Turkey") %>%
  ggplot(aes(x=year, y=lifeExp))+
  geom_point()
```

see the figure @ref(fig:gg-oz-gapminder)

As an example, I used the following paper: [@arcelli1997]

## References

[@arcelli1997]
